A Tutorial on Tailored Simulation-Based Sample Size Planning for Experimental Designs with Generalized Linear Mixed Models

### 2024-07-01 manuscript.qmd
fix yu reference again...

packagetable <- data.frame(
  col1 = c("glmmrBase", "longpower", "mixedpower", "mlmpower", "pamm", "pass.lme", "PowerAnalysisIL", "powerlmm", "simglm", "simr", "summary_statistics based_power", "WebPower"),
  col2 = c("Formula- and simulation-based power analysis; non-linear fixed effects and flexible covariance functions",
              "Formula-based power analysis; focus on longitudinal data",
              "Simulation-based power analysis; based on 'simr' package",
              "Simulation-based power analysis; missing data mechanisms",
              "Simulation-based power analysis; based on 'lme4' package",
              "Formula-based power analysis; limited documentation",
              "Simulation-based power analysis; focus on longitudinal data",
              "Simulation-based power analysis; missing data mechanisms; focus on longitudinal data",
              "Simulation-based power analysis; missing data mechanisms",
              "Simulation-based power analysis; based on 'lme4' package",
              "Summary-statistics-based power analysis; based on 'pwr' package",
              "Formula-based power analysis; based on 'longpower' package; focus on longitudinal data"),
  col3 = c("no", "[yes](https://atrihub.shinyapps.io/power/)", "no", "no", "no", "no", "[yes](https://github.com/ginettelafit/PowerAnalysisIL?tab=readme-ov-file#shiny-app-and-r-package-to-perform-power-analysis-to-select-the-number-of-participants-in-intensive-longitudinal-studies)", "[yes](https://github.com/rpsychologist/powerlmm?tab=readme-ov-file#launch-interactive-web-application)", "[yes](https://simglm.brandonlebeau.org/reference/run_shiny.html)", "no", "[yes](https://koumurayama.shinyapps.io/summary_statistics_based_power/)", "[yes](https://webpower.psychstat.org/wiki/start)"),
  col4 = c("yes", "no", "yes", "no", "no", "no", "no", "no", "yes", "yes", "yes", "no"),
  col5 = c("none", "limited set of study designs with two levels", "none", "limited to two levels", "none", "none", "limited set of study designs with two levels", "limited set of study designs with two or three levels", "limited to two or three levels", "none", "limited set of study designs with two levels", "limited set of study designs with two levels"),
  col6 = c("@watsonGeneralisedLinearMixed2023", "@iddiPowerSampleSize2022", "@kumleEstimatingPowerGeneralized2021", "@endersSimpleMonteCarlo2023", "@martinMeasuringIndividualDifferences2011", "@yumarcoPassLmePower2019", "@lafitSelectionNumberParticipants2021", "@magnussonConsequencesIgnoringTherapist2018", "@lebeauPowerAnalysisSimulation2019", "@greenSIMRPackagePower2016", "@murayamaSummarystatisticsbasedPowerAnalysis2022", "@zhangPracticalStatisticalPower2018")
)
names(packagetable) <- c("Package name", "Summary", "GUI available", "GLMM support", "Design limitations", "Reference")

>>>>

packagetable <- data.frame(
  col1 = c("glmmrBase", "longpower", "mixedpower", "mlmpower", "pamm", "pass.lme", "PowerAnalysisIL", "powerlmm", "simglm", "simr", "summary_statistics based_power", "WebPower"),
  col2 = c("Formula- and simulation-based power analysis; non-linear fixed effects and flexible covariance functions",
              "Formula-based power analysis; focus on longitudinal data",
              "Simulation-based power analysis; based on 'simr' package",
              "Simulation-based power analysis; missing data mechanisms",
              "Simulation-based power analysis; based on 'lme4' package",
              "Formula-based power analysis; limited documentation",
              "Simulation-based power analysis; focus on longitudinal data",
              "Simulation-based power analysis; missing data mechanisms; focus on longitudinal data",
              "Simulation-based power analysis; missing data mechanisms",
              "Simulation-based power analysis; based on 'lme4' package",
              "Summary-statistics-based power analysis; based on 'pwr' package",
              "Formula-based power analysis; based on 'longpower' package; focus on longitudinal data"),
  col3 = c("no", "[yes](https://atrihub.shinyapps.io/power/)", "no", "no", "no", "no", "[yes](https://github.com/ginettelafit/PowerAnalysisIL?tab=readme-ov-file#shiny-app-and-r-package-to-perform-power-analysis-to-select-the-number-of-participants-in-intensive-longitudinal-studies)", "[yes](https://github.com/rpsychologist/powerlmm?tab=readme-ov-file#launch-interactive-web-application)", "[yes](https://simglm.brandonlebeau.org/reference/run_shiny.html)", "no", "[yes](https://koumurayama.shinyapps.io/summary_statistics_based_power/)", "[yes](https://webpower.psychstat.org/wiki/start)"),
  col4 = c("yes", "no", "yes", "no", "no", "no", "no", "no", "yes", "yes", "yes", "no"),
  col5 = c("none", "limited set of study designs with two levels", "none", "limited to two levels", "none", "none", "limited set of study designs with two levels", "limited set of study designs with two or three levels", "limited to two or three levels", "none", "limited set of study designs with two levels", "limited set of study designs with two levels"),
  col6 = c("@watsonGeneralisedLinearMixed2023", "@iddiPowerSampleSize2022", "@kumleEstimatingPowerGeneralized2021", "@endersSimpleMonteCarlo2023", "@martinMeasuringIndividualDifferences2011", "@yuPassLmePower2019", "@lafitSelectionNumberParticipants2021", "@magnussonConsequencesIgnoringTherapist2018", "@lebeauPowerAnalysisSimulation2019", "@greenSIMRPackagePower2016", "@murayamaSummarystatisticsbasedPowerAnalysis2022", "@zhangPracticalStatisticalPower2018")
)
names(packagetable) <- c("Package name", "Summary", "GUI available", "GLMM support", "Design limitations", "Reference")
